Different rules for binocular combination of luminance in cortical and subcortical pathways

### 2022-09-30 manuscript.Rmd
Small edits

Looking at the results for the 48 % contrast condition, we can observe that, when the ratio in both eyes was set to be one, the target appeared to have the same flickering intensity as the standard when the contrast in both eyes was selected to be, on average, 50 % (red line). This is also observable for the 24 % contrast condition, where the target appeared to have the same flickering intensity when the contrast was selected to be around 25 %. These two results show that the paradigm was working correctly and that the participants could see the flicker properly.
When the ratio was set to be 0 in one of the two eyes, we observe that, for the target to appear to flicker similarly to the standard, the contrast in the other eye was set to be around double the contrast of the standard. For the 48 % contrast, when the ratio in the right eye was 0, the contrast in the left eye was around 90 %, while, when the ratio in the left eye was 0, contrast in the right eye was around 96 %. For the 24 % contrast, when the ratio in the right eye was 0, the contrast in the left eye was around 57 %, while, when the ratio in the left eye was 0, contrast in the right eye was around 50 %. When looking at the rest of the data, we can see that the points, for both contrast conditions, seem to fall along the line representing a linear combination model, with the results for the 24 % condition showing a very strong summation that seem to exceed this linear combination. Overall, these results seem to suggest that the processing of temporal luminance modulations seems to follow near linear combination rules, which is in line with our results from experiment 1.

>>>>

Looking at the results for the 48 \% contrast condition, we can observe that, when the ratio in both eyes was set to be one, the target appeared to have the same flickering intensity as the standard when the contrast in both eyes was selected to be, on average, 50 \% (red line). This is also observable for the 24 \% contrast condition, where the target appeared to have the same flickering intensity when the contrast was selected to be around 25 \%. These two results show that the paradigm was working correctly and that the participants could see the flicker properly.
When the ratio was set to be 0 in one of the two eyes, we observe that, for the target to appear to flicker similarly to the standard, the contrast in the other eye was set to be around double the contrast of the standard. For the 48 \% contrast, when the ratio in the right eye was 0, the contrast in the left eye was around 90 \%, while, when the ratio in the left eye was 0, contrast in the right eye was around 96 \%. For the 24 \% contrast, when the ratio in the right eye was 0, the contrast in the left eye was around 57 \%, while, when the ratio in the left eye was 0, contrast in the right eye was around 50 \%. When looking at the rest of the data, we can see that the points, for both contrast conditions, seem to fall along the line representing a linear combination model, with the results for the 24 \% condition showing a very strong summation that seem to exceed this linear combination. Overall, these results seem to suggest that the processing of temporal luminance modulations seems to follow near linear combination rules, which is in line with our results from experiment 1.
